## Environmental stressors {#strportrait}

```{r stresssetup, echo = FALSE}
st <- read.csv("../data/data-metadata/metadata_stresseurs.csv")
```

Characterization of environmental stressors in the study area resulted in the description of `r length(unique(st$stresseur))` stressors divided into `r nrow(st)` subcategories that are considered for the cumulative effects assessment of marine activities (Table \@ref(tab:stress)). The following sections present the data, methods, and results of the data integration allowing us to characterize the environmental stressors in the study area.

<br/>

```{r stress}
tab <- select(st, title, francais, description, source)
tab$title[duplicated(tab$title)] <- ""
uid <- which(tab$title != "")[-1]-1
tab$source <- gsub(",", ", ", tab$source)

tab %>%
  knitr::kable(
    col.names = c("Environmental stressors", "Subcategories", "Description", "Source"),
    row.names = FALSE,
    caption = "
    List of environmental stressor subcategories considered for the cumulative effects assessment of marine activities in the St. Lawrence and the Saguenay river. See [Appendix 1](#annexe1) for more details on data sources."
  ) #%>%
  #kableExtra::row_spec(uid, extra_css = "border-bottom: 2px solid")
```

<br/>
