### Areas of cultural, heritage and archeological interest {#site}

```{r site_setup, echo = FALSE}
meta <- read_yaml("../data/data-metadata/int_cv_site.yml")
```

The St. Lawrence and Saguenay rivers constitute a system of major cultural, heritage and archeological importance for the First Nations and the coastal communities. Areas of cultural, heritage and archeological interest were therefore identified as a valued component to be considered in the pilot project to assess the cumulative effects of marine activities. The areas of interest characterized are mainly provided by the First Nations, as well as heritage sites listed in public registers and protected areas in the region. This results in a total of `r length(meta$dataDescription$categories$accronyme)` distinct categories of areas of interest (Table \@ref(tab:siteCat)). Data characterizing the areas of interest were incorporated directly into the study grid as presence-absence. The following sections describe the data used to develop a profile of cultural, heritage and archeological areas of interest in the study area.

<br/>

```{r siteCat}
tab <- as.data.frame(meta$dataDescription$categories)
tab <- arrange(tab, type, francais)
tab <- select(tab, type, francais)

uid <- logical(nrow(tab)) 
for(i in 2:length(uid)) uid[i] <- ifelse(tab$type[i] == tab$type[i-1], TRUE, FALSE)

tab$type[uid] <- ""  
  
tab %>%
  knitr::kable(
    col.names = c("Sites d'intérêt","Catégories"),
    row.names = FALSE,
    caption = "Catégories de sites d'intérêt culturels, patrimoniaux et archéologiques identifiés pour le Saint-Laurent et le Saguenay."
  )
```

<br/>
